---
title: "Basics_with_R"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#create a varibale that stores 1000 random numbers picked from a normal distribution with params (0,1)
x <- rnorm(1000)

#plot using a histogram
hist(x)
```

```{r}
#lets see the average precipitation in 70 cities in the US using a standard R dataframe that you don't even need to load
hist(precip,col = "steelblue")

```

#70 cities are the population of interest.
#precipitation is the variable of interest.
#Let's calculate the mean of the means. Thus, mean here is the parameter of interest.

```{r}
mean(precip)
sd(precip)
```

However, in real life, it is impossible to collect all the samples of a population. Hence we sample a certain subset of the population and use this subset as a representative of the population and calculate necessary values such as mean/ median income, precipitation, expenditure, grade, age, etc. When we use the sample instead of the population, we call it statistic rather than a parameter.

Statistical Inference: We can use the sample to infer properties of the population so long as observations are sampled at random from the population of interest.

```{r}
#Calculate the % of samples in a normal distribution with mean 20 and stdev 3 below the value of 15
pnorm(15, mean = 20, sd = 3)

```
Roughly 4.7% of the samples will be less than 15 in this normal distribution.




